Title

### 2021-07-28 latex-slides/slides.tex
Add purple color

\begin{frame}{Components}{Colors}
    {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
    {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline
    {\color{ruby} Test sentence with \textbackslash color\{ruby\}}\newline
    {\color{alice} Test sentence with \textbackslash color\{alice\}}\newline
    {\color{daisy} Test sentence with \textbackslash color\{daisy\}}\newline
    {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
    {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
    {\color{asher} Test sentence with \textbackslash color\{asher\}}\newline
\end{frame}

>>>>

\begin{frame}{Components}{Colors}
    {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
    {\color{purple} Test sentence with \textbackslash color\{purple\}}\newline
    {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline
    {\color{ruby} Test sentence with \textbackslash color\{ruby\}}\newline
    {\color{alice} Test sentence with \textbackslash color\{alice\}}\newline
    {\color{daisy} Test sentence with \textbackslash color\{daisy\}}\newline
    {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
    {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
    {\color{asher} Test sentence with \textbackslash color\{asher\}}\newline
\end{frame}
